### 2017-01-05 Chapters/theory.tex
Last corrections from hans, also add list of figures and tables

\begin{figure}[p]
\centering
\includegraphics[width=0.7\textwidth]{./Fig/FigS4-1}
\caption[ppGpp concentration is a function of total ribosome and amino acid concentrations.]
{
{\bf ppGpp concentration is a function of total ribosome and amino acid concentrations.}\newline
We assume the dynamics of ppGpp to be fast on the time-scale of changes in the ribosome and amino acid concentrations.
The concentration of ppGpp can thus be expressed as a function of the latter two variables, using the model of Bosdriesz \textit{et al.}~\cite{bosdriesz_how_2015}.
Parameters are taken from Table~\ref{tab:notations}.
}
\label{fig:ppGpp}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{./Fig/plot_strategies}
\caption{
\noindent\textit{A:} Nutrient-only strategy: $\alpha = f(E_M)$.
The dashed, black curve is the (unique) strategy driving the system exactly to the optimal steady state, that is, the state in which growth occurs at the maximal rate supported by $E_M$.
The function $f$ is defined by Eq.~\ref{eq:meth_f} in the \textit{Methods} section of the main text.
The solid, red curve is an approximation of this function by the simple Michaelis-Menten curve of Eq.~\ref{eq:MMApprox}, with $K_{mE} = 1.0$.
\textit{B:} Precursor-only strategy: $\alpha = g(\hat{p})$.
The dashed, black curve is the (unique) strategy driving the system exactly to the optimal steady state.
The function $g$ is defined by Eq.~\ref{eq:meth_g} in the \textit{Methods} section of the main text.
The solid, red curve is an approximation of this function by the simple Hill curve of Eq.~\ref{eq:HillApprox}, with $K_{mp} = 0.06$ and a cooperativity coefficient 2.}
\end{figure}

>>>>

\begin{figure}[p]
\centering
\includegraphics[width=0.7\textwidth]{./Fig/FigS4-1}
\caption{
\textbf{ppGpp concentration is a function of total ribosome and amino acid concentrations.}
We assume the dynamics of ppGpp to be fast on the time-scale of changes in the ribosome and amino acid concentrations.
The concentration of ppGpp can thus be expressed as a function of the latter two variables, using the model of Bosdriesz \textit{et al.}~\cite{bosdriesz_how_2015}.
Parameters are taken from Table~\ref{tab:notations}.
}
\label{fig:ppGpp}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{./Fig/plot_strategies}
\caption{
\textbf{Simple control strategies for the self-replicator of bacterial growth.}
\textit{A:} Nutrient-only strategy: $\alpha = f(E_M)$.
The dashed, black curve is the (unique) strategy driving the system exactly to the optimal steady state, that is, the state in which growth occurs at the maximal rate supported by $E_M$.
The function $f$ is defined by Eq.~\ref{eq:meth_f} in the \textit{Methods} section of the main text.
The solid, red curve is an approximation of this function by the simple Michaelis-Menten curve of Eq.~\ref{eq:MMApprox}, with $K_{mE} = 1.0$.
\textit{B:} Precursor-only strategy: $\alpha = g(\hat{p})$.
The dashed, black curve is the (unique) strategy driving the system exactly to the optimal steady state.
The function $g$ is defined by Eq.~\ref{eq:meth_g} in the \textit{Methods} section of the main text.
The solid, red curve is an approximation of this function by the simple Hill curve of Eq.~\ref{eq:HillApprox}, with $K_{mp} = 0.06$ and a cooperativity coefficient 2.}
\end{figure}
